Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-12 outputs/paper/paper.qmd
update

# Plotting the data with scatter plot and trend line
ggplot(data, aes(x = year, y = brate_all)) +
  geom_point(color = "skyblue") +
  geom_smooth(method = "lm", se = FALSE, color = "pink") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  annotate("text", x = 2009, y = 70, label = "2007", vjust = -0.5, hjust = 0.5, color = "black") +
  geom_hline(yintercept = seq(50, 80, by = 5), color = "lightgrey") +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) +
  labs(x = "Year", y = "Births per 1,000 women age 15-44",
       caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019, and 2020.") +
  theme_classic()
```

>>>>

# Plotting the data with scatter plot and trend line
ggplot(data, aes(x = year, y = brate_all)) +
  geom_point(color = "pink") +
  geom_smooth(method = "lm", se = FALSE, color = "skyblue") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  annotate("text", x = 2009, y = 70, label = "2007", vjust = -0.5, hjust = 0.5, color = "black") +
  geom_hline(yintercept = seq(50, 80, by = 5), color = "lightgrey") +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  scale_x_continuous(limits = c(1980, 2020), breaks = seq(1980, 2020, by = 1), labels = function(x) ifelse(x %% 5 == 0, x, "")) +
  labs(x = "Year", y = "Births per 1,000 women age 15-44",
       caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019, and 2020.") +
  theme_classic()
```
